### 2023-03-16 main.tex
fixed

\section{Duality}

@@

\subsection{Absorption probabilities for general 2j}

>>>>

\section{Duality}\label{sectionDuality}

@@

{\color{blue}An application of duality is to compute the moments of the steday state of the the original process. Indeed, as metioned in subsection \ref{}, the dual process voids the chain. Therefore, the problem of computing the moments with respect to the stationary distribution is reduced to computing the absorption probabilities of dual particles. \\
Calling $\mu_{stat}$ the stationary measure of the the process \eqref{Generator} starting from a configuration $\bm{n}$, we can write the following chain of equalities
\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\bm{\xi})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{k}}\left(\frac{\beta_{k}}{\beta_{1}+\ldots+\beta_{N}}\right)^{|\xi_{k}|-i_{k}}
we denote by $i_{k}$ the number of dual particles of species $k\in\{2,\ldots,N\}$ absorbed at left and by $|\xi_{k}|-i_{k}$ the number of particles absorbed at right. \\}
